\documentclass{article}
\begin{document}

\section{Status quo}

As at 0.78 there is an unfortunate mish-mash of code to handle the
input `content' the goes into a DCP.

The Film has a `content' file name.  This is guessed to be either a
movie (for FFmpeg) or a still-image (for ImageMagick) based on its
extension.  We also have `external audio', which is a set of WAV files
for libsndfile, and a flag to enable that.

The `content' file is badly named and limiting.  We can't have
multiple content files, and it's not really the `content' as such (it
used to be, but increasingly it's only a part of the content, on equal
footing with `external' audio).

The choice of sources for sound is expressed clumsily by the
AudioStream class hierarchy.


\section{Targets}

We want to be able to implement the following:

\begin{itemize}
\item Immediately:
\begin{itemize}
\item Multiple still images, each with their own duration, made into a `slide-show'
\item Lack of bugs in adding WAV-file audio to still images.
\item External subtitle files (either XML or SRT) to be converted to XML subtitles in the DCP.
\end{itemize}

\item In the future:
\begin{itemize}
\item Playlist-style multiple video / audio (perhaps).
\end{itemize}
\end{itemize}


\section{Content hierarchy}

One idea is to have a hierarchy of Content classes (\texttt{Content},
\texttt{\{Video/Audio\}Content}, \texttt{FFmpegContent}, \texttt{ImageMagickContent},
\texttt{SndfileContent}).

Then the Film has a list of these, and decides what to put into the
DCP based on some rules.  These rules would probably be fixed (for
now), with the possibility to expand later into some kind of playlist.


\section{Immediate questions}

\subsection{What Film attributes are video-content specific, and which are general?}

Questionable attributes:

\begin{itemize}
\item Trust content header
\item Crop
\item Filters

Post-processing (held as part of the filters description) is done in
the encoder, by which time all knowledge of the source is lost.

\item Scaler
\item Trim start/end

Messily tied in with the encoding side.  We want to implement this
using start/end point specifications in the DCP reel, otherwise
modifying the trim points requires a complete re-encode.

\item Audio gain
\item Audio delay
\item With subtitles
\item Subtitle offset/scale
\item Colour LUT
\end{itemize}

Attributes that I think must remain in Film:
\begin{itemize}
\item DCP content type
\item Format
\item A/B
\item J2K bandwidth
\end{itemize}

Part of the consideration here is that per-content attributes need to
be represented in the GUI differently to how things are represented
now.

Bear in mind also that, as it stands, the only options for video are:

\begin{enumerate}
\item An FFmpeg video
\item A set of stills
\end{enumerate}

and so the need for multiple scalers, crop and filters is
questionable.  Also, there is one set of audio (either from WAVs or
from the FFMpeg file), so per-content audio gain/delay is also
questionable.  Trust content header is only applicable for FFmpeg
content, really.  Similarly trim, with-subtitles, subtitle details,
colour LUT; basically none of it is really important right now.

Hence it may be sensible to keep everything in Film and move it later
along YAGNI lines.


\subsection{Who answers questions like: ``what is the length of video?''?}

If we have FFmpeg video, the question is easy to answer.  For a set of
stills, it is less easy.  Who knows that we are sticking them all
together end-to-end, with different durations for each?

If we have one-content-object equalling one file, the content objects
will presumably know how long their file should be displayed for.
There would appear to be two options following this:

\begin{enumerate}
\item There is one \texttt{ImageMagickDecoder} which is fed all the
  files, and outputs them in order.  The magic knowledge is then
  within this class, really.
\item There are multiple \texttt{ImageMagickDecoder} classes, one per
  \texttt{..Content}, and some controlling (`playlist') class to manage
  them.  The `playlist' is then itself a
  \texttt{\{Video/Audio\}Source}, and has the magic knowledge.
\end{enumerate}


\section{Playlist approach}

Let's try the playlist approach.  We define a hierarchy of content classes:

\begin{verbatim}

class Content
{
public:
  boost::filesystem::path file () const;
};

class VideoContent : virtual public Content
{
public:
  VideoContentFrame video_length () const;
  float video_frame_rate () const;
  libdcp::Size size () const;

};

class AudioContent : virtual public Content
{

};

class FFmpegContent : public VideoContent, public AudioContent
{
public:
  .. stream stuff ..
};

class ImageMagickContent : public VideoContent
{

};

class SndfileContent : public AudioContent
{
public:
  .. channel allocation for this file ..
};
\end{verbatim}

Then Film has a \texttt{Playlist} which has a
\texttt{vector<shared\_ptr<Content>}.  And it can answer questions
about audio/video length, frame rate, audio channels and so on.

\texttt{Playlist} can also be a source of video and audio, so clients can do:

\begin{verbatim}
shared_ptr<Playlist> p = film->playlist ();
p->Video.connect (foo);
p->Audio.connect (foo);
while (!p->pass ()) {
  /* carry on */
}
\end{verbatim}

Playlist could be created on-demand for all the difference it would make.

\end{document}
