\documentclass{article}
\title{KDM timezones}
\author{}
\date{}
\begin{document}
\maketitle

KDMs have their valid-from and to times expressed as a local time, with a timezone that tells you the offset from UTC.

There have been various different UXs in DCP-o-matic to specify the timing and time zone for KDMs, and some discussion
about the best way.

Initially cinemas in DCP-o-matic had timezones.  Then the KDM UI would get local time, and it would be written to the
KDMs with the appropriate timezone for the cinema.

This was changed in \#2300 to remove timezone from the cinema and instead the KDM UI gets a local time with a time zone
(e.g. 14:00 UTC+2) then the KDMs are written in UTC (i.e.\ 12:00) with the -00:00 timezone (meaning `unknown').

The reason for this was that cinema timezones change with DST etc., people don't want to change them all the time, and
we don't want to try managing DSTs automatically.

Then people said that this was no good, as DST is not a concern (KDMs shouldn't be issued so tightly that they could
be messed up by DST errors) but timezones are definitely a concern as they can be up to 12 hours.

Then in \#2473 it was changed so that cinemas once again have timezone but the KDM timezone is set by the KDM UI.
The KDM UI timezone is prefilled with the cinema timezone, \emph{but only if that timezone is unique}.  If multiple
cinemas are selected the default KDM UX timezone is UTC.

Then Bert says this is no good because he makes KDMs for two different cinemas, one at UTC+9 and one at UTC+11.
The cinemas look at the times and see the UTC (-00:00) times and think they are wrong.

Unfortunately I can't now remember who had the problem with DST, as it seems it was probably pretty close to correct
in the first place.

\end{document}
